CA of Music Genre Stereotypes

### 2025-06-21 Old/analysis-bb-old.qmd
moving

```{r Creating individual matrices}
   row.breiger <- function(x) {
      x %*% t(x)
      }
   col.breiger <- function(x) {
      t(x) %*% x
      }
   bb <- function(x) {
      x <- suppressMessages(disparity(x, alpha = 0.25, narrative = FALSE))
      return(x)
      }
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .9 | den < 0.1)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, function(x) {matrix(as.numeric(x), 20, 15, byrow = TRUE)}) # creating individual two mode network of genre by labels
      r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "Alt_Rock", "Dance", "Metal")
       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   ind.row <- lapply(ind.mat, row.breiger) # individual genre projection
   ind.col <- lapply(ind.mat, col.breiger) # individual label projection
   row.bb <- lapply(ind.row, bb)
   col.bb <- lapply(ind.col, bb)
   row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(col.bb), ncol = 15, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- r # naming genre stacked matrix columns
   colnames(col.stack) <- c # naming label stacked matrix columns
   rownames(row.stack) <- rep(r, nrow(dat2)) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, nrow(dat2)) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
   names(ind.row) <- dat$id_char[-c(bad.den)]
   names(ind.col) <- dat$id_char[-c(bad.den)]
   names(row.bb) <- dat$id_char[-c(bad.den)]
   names(col.bb) <- dat$id_char[-c(bad.den)]
```

@@

```{r Plot Data}
     make.plot.dat <- function(x) { 
         w <-  data.frame(x) %>% 
         mutate(col.obj = gsub("\\..*","",rownames(x))) 
         rownames(w) <- 1:nrow(x)
         return(w)
         }
      col.gen.dat <-  data.frame(CA.r$col$coord) %>% 
         mutate(col.obj = rownames(CA.r$col$coord)) #genre column scores
      col.lab.dat <-  data.frame(CA.c$col$coord) %>% 
         mutate(col.obj = rownames(CA.c$col$coord)) #label column scores
      sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
      sup.gen.dat <- data.frame(sup.gen.dat, 
                                col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
      rownames(sup.gen.dat) <- sup.gen.dat$col.obj
      sup.lab.dat <- data.frame(sup.lab.dat, 
                                col.obj = gsub("label.", "", rownames(sup.lab.dat)))
      rownames(sup.lab.dat) <- sup.lab.dat$col.obj
      row.gen.dat <- make.plot.dat(CA.r$row$coord) #genre row scores
      row.lab.dat <- make.plot.dat(CA.c$row$coord) #label row scores
   ind.gen.sup <- CA.r$quali.sup$coord %>% 
      data.frame() %>% 
      slice(21:nrow(CA.r$quali.sup$coord)) 
   ind.gen.sup$id_char <- str_sub(rownames(ind.gen.sup), 4, -1)
   ind.lab.sup <- CA.c$quali.sup$coord %>% 
      data.frame() %>% 
      slice(21:nrow(CA.c$quali.sup$coord)) 
   ind.lab.sup$id_char <- str_sub(rownames(ind.lab.sup), 4, -1)
```

>>>>

```{r Creating individual matrices}
   make.mat <- function(x) {
      x <- matrix(as.numeric(x), 20, 15, byrow = TRUE)
      return(x)
   }
   row.breiger <- function(x) {
      x <- x %*% t(x)
      return(x)
      }
   col.breiger <- function(x) {
      x <- t(x) %*% x
      return(x)
      }
   bb <- function(x, a = 0.25) {
      x <- suppressMessages(disparity(x, alpha = a, narrative = FALSE))
      return(x)
      }
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .9 | den < 0.1)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, make.mat) # creating individual two mode network of genre by labels
      r <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big_Band", "Classic_Rock", "Country", "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", "Pop", "Contemp_Rock", "Alt_Rock", "Dance", "Metal")
       c <- c("Female", "Male", "White", "Black", "Hispanic", "Asian", "College", "No_College", "Young", "Mid_Age", "Old", "Lower_Class", "Working_Class", "Middle_Class", "Upper_Class")
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   ind.row <- lapply(ind.mat, row.breiger) # individual genre projection
   ind.col <- lapply(ind.mat, col.breiger) # individual label projection
   row.bb <- lapply(ind.row, bb)
   col.bb <- lapply(ind.col, bb)
   row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(col.bb), ncol = 15, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- r # naming genre stacked matrix columns
   colnames(col.stack) <- c # naming label stacked matrix columns
   rownames(row.stack) <- rep(r, nrow(dat2)) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, nrow(dat2)) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
   names(ind.row) <- dat$id_char[-c(bad.den)]
   names(ind.col) <- dat$id_char[-c(bad.den)]
   names(row.bb) <- dat$id_char[-c(bad.den)]
   names(col.bb) <- dat$id_char[-c(bad.den)]
```

@@

```{r Plot Data}
     make.plot.dat <- function(x) { 
         w <-  data.frame(x) %>% 
         mutate(col.obj = gsub("\\..*","",rownames(x))) 
         rownames(w) <- 1:nrow(x)
         return(w)
         }
      #genre column scores data frame
      col.gen.dat <-  data.frame(CA.r$col$coord) %>% 
         mutate(col.obj = rownames(CA.r$col$coord)) 
      #label column scores data frame
      col.lab.dat <-  data.frame(CA.c$col$coord) %>% 
         mutate(col.obj = rownames(CA.c$col$coord)) 
      #supplementary scores data frame for genres
      sup.gen.dat <- CA.r$quali.sup$coord[1:20, ] 
      sup.gen.dat <- data.frame(sup.gen.dat, 
                                col.obj = gsub("genre.", "", rownames(sup.gen.dat)))
      rownames(sup.gen.dat) <- 1:nrow(sup.gen.dat)
      #supplementary scores data frame for labels
      sup.lab.dat <- CA.c$quali.sup$coord[1:15, ] 
      sup.lab.dat <- data.frame(sup.lab.dat, 
                                col.obj = gsub("label.", "", rownames(sup.lab.dat)))
      rownames(sup.lab.dat) <- 1:nrow(sup.lab.dat)
      #genre row scores
      row.gen.dat <- make.plot.dat(CA.r$row$coord) 
      #label row scores
      row.lab.dat <- make.plot.dat(CA.c$row$coord) 
      #supplementary individual scores for genres
      ind.gen.sup <- CA.r$quali.sup$coord %>% 
         data.frame() %>% 
         slice(21:nrow(CA.r$quali.sup$coord)) %>% 
         mutate(id_char = str_sub(rownames(ind.gen.sup), 4, -1))
      row.names(ind.gen.sup) <- 1:nrow(ind.gen.sup)
      #supplementary individual scores for labels
      ind.lab.sup <- CA.c$quali.sup$coord %>% 
         data.frame() %>% 
         slice(16:nrow(CA.c$quali.sup$coord)) %>% 
         mutate(id_char = str_sub(rownames(ind.lab.sup), 4, -1))
      row.names(ind.lab.sup) <- 1:nrow(ind.lab.sup)
```

```{r Cloud Variance Functions}
   check.cloud.var <- function()

```
